---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DiDCov

<!-- badges: start -->
<!-- badges: end -->

**DiDCov** is an R package designed to assist researchers and analysts working with Difference-in-Differences (DiD) estimations. It provides tools for constructing variance-covariance matrices for DiD estimates, accommodating both constant and time-decaying correlations between periods.

## Installation

You can install the development version of DiDCov from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jespernwulff/DiDCov")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(DiDCov)

#Example 1: Using a specified decay parameter (exponential decay)
years <- c(2008, 2009, 2010, 2011)
variances <- c(0.0001, 0.0002, 0.00015, 0.00012)
decay_param <- 0.1
result_exp <- construct_cov_matrix_decay(
   years = years,
   variances = variances,
   decay_type = "exponential",
   decay_param = decay_param
)
print(result_exp$cov_matrix)
print(result_exp$decay_param)
```
