---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# DiDCov

<!-- badges: start -->
<!-- badges: end -->

**DiDCov** is an R package designed to assist researchers and analysts working with Difference-in-Differences (DiD) estimations. It provides tools for constructing variance-covariance matrices for DiD estimates, accommodating both constant and time-decaying correlations between periods.

The package is currently experimental and under development. 

## Installation

You can install the development version of DiDCov from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jespernwulff/DiDCov")
```

## Example

**Example 1: Constructing a Covariance Matrix with a Specified Rho**

The `construct_cov_matrix` function creates a covariance matrix using a constant correlation coefficient (`rho`) for all off-diagonal elements.

```{r example}
library(DiDCov)

years <- c(2008, 2009, 2010, 2011, 2012, 2014, 2015)
variances <- c(0.000104, 0.000067, 0.00008, 0.000067, 0.000059, 0.000063, 0.000063)

# Specify the correlation coefficient
rho_value <- 0.8

# Construct the covariance matrix
cov_matrix <- construct_cov_matrix(years, variances, rho = rho_value)

# Display the covariance matrix
print(cov_matrix)
```

**Explanation**:

* The diagonal elements are the variances.
* The off-diagonal elements are calculated using the specified rho and the standard deviations of the variances.
* This covariance matrix assumes a constant correlation of 0.8 between all pairs of years.

**Example 2: Constructing a Covariance Matrix with Exponential Decay**

The `construct_cov_matrix_decay` function creates a covariance matrix where the correlation between years decays exponentially based on the time difference and a decay parameter `lambda`.

```{r}
# Specify the decay parameter
lambda_exp <- 0.5  # Controls the rate of exponential decay

# Construct the covariance matrix with exponential decay
cov_matrix_exp <- construct_cov_matrix_decay(years, variances, 
                                             decay_type = "exponential", 
                                             lambda = lambda_exp)

# Display the covariance matrix
print(cov_matrix_exp)
```

**Explanation**:

* The correlation between years decreases exponentially as the time difference increases.
* The lambda parameter controls how quickly the correlation decays. A larger lambda results in a faster decay.
* This covariance matrix reflects the assumption that observations closer in time are more strongly correlated.

**Example 3: Constructing a Covariance Matrix with Linear Decay**

Alternatively, you can use linear decay where the correlation decreases linearly with time difference until it reaches zero.

```{r}
# Specify the decay parameter
lambda_lin <- 0.2  # Controls the rate of linear decay

# Construct the covariance matrix with linear decay
cov_matrix_lin <- construct_cov_matrix_decay(years, variances, 
                                             decay_type = "linear", 
                                             lambda = lambda_lin)

# Display the covariance matrix
print(cov_matrix_lin)
```

**Explanation**: 

* The correlation decreases linearly with the time difference.
* The lambda parameter controls the rate of decay. Here, a lambda of 0.2 causes the correlation to reach zero for time differences greater than 5 units.
* Notice that correlations are zero for years that are sufficiently far apart.

